---
title: "Health Care Fraud EDA"
output: html_notebook
---

```{r}
library(tidyverse)

docs = read_csv('../data/combinedData.csv');
target = read_csv('../data/combinedTarget.csv');

target = select(target, Provider, PotentialFraud, color, Set) %>% data.frame()

data = docs %>% 
  left_join(target, by=c('Provider','Set')) %>% 
  select(-c('X1.x','X1.y')) %>% replace_na(0);
```
netAnal takes in the data, state number, and counties and produces a bipartites network
graph of either the

- Provider-Patient Network (type = 'propat')
- Provider-Doctor Network (type = 'prodoc')
- Patient-Doctor Network (type = 'patdoc')

User can also specify the way to layout the diagram. Usually 'stress' is the best layout to visualize these networks. For a more hierarchical layout try 'sugiyama'.

User can also look at all counties within a given state by setting county = 'all'.
Though for large states or patdoc networks this is not recommended since it takes a long time to plot and graphs are not that informative. 


```{r}
source("getNet.R")



bnet = propat(data, c('Oklahoma'), 100)

#plotProDoc(bnet, layout = 'stress')

plot(log(degree.distribution(bnet)),
     type="b",xlab="Degree",ylab="Proportion")

#ggsave(filename=paste0('../visualizations/networks/texas100_patdoc_stress.png'),plot=last_plot())
op <- par(mfrow=c(1,2)) 
plot(degree.distribution(bnet),xlab="Degree", ylab="Proportion") 
plot(degree.distribution(g), xlab="Degree",ylab="Proportion") 
par(op)
```

```{r}

deglist = list()
annlist = list()
btwnlist = list()
eigenlist = list()

for (state in data$State %>% unique()) {
    # Get Provider-Patient Network for all counties in the state
    bnet = propat(data, state, 'all')
    # Project bipartite network into two one mode networks
    bn.pr <- bipartite.projection(bnet)
    # Get Provider network - affiliated through shared patients
    bn.provider <- bn.pr$proj2
    
    # Calculate Degrees
    deg = degree(bn.provider)
    deg = tibble(names(deg), deg)
    colnames(deg) = c('Provider','Degree')
    
    # Calculate Betweeenness
    btwn = betweenness(bn.provider)
    btwn = tibble(names(btwn), btwn)
    colnames(btwn) = c('Provider','Betweenness')
    
    # Calculate Values of the First Eigenvector of the Graph Matrix
    eign = eigen_centrality(bn.provider)$vector
    eign = tibble(names(eign), eign)
    colnames(eign) = c('Provider','Eigenvector')
    
    # Calculate Average Nearest Neighbors
    ann = knn(bn.provider)
    ann = ann$knn
    ann = tibble(names(ann), ann)
    colnames(ann) = c('Provider','Avg.NN')
    
    # Add to list by state
    deglist[[state]] = deg
    btwnlist[[state]] = btwn 
    eigenlist[[state]] = eign 
    annlist[[state]] = ann 
}

propatDeg <- dplyr::bind_rows(deglist)
propatBtwn <- dplyr::bind_rows(btwnlist)
propatEign <- dplyr::bind_rows(eigenlist)
propatANN <- dplyr::bind_rows(annlist)

#############################################################################

deglist = list()
annlist = list()
btwnlist = list()
eigenlist = list()

for (state in data$State %>% unique()) {
    # Get Provider-Doctor Network for all counties in the state
    bnet = prodoc(data, state, 'all')
    # Project bipartite network into two one mode networks
    bn.pr <- bipartite.projection(bnet)
    # Get Provider network - affiliated through shared doctors
    bn.provider <- bn.pr$proj2
    
    # Calculate Degrees
    deg = degree(bn.provider)
    deg = tibble(names(deg), deg)
    colnames(deg) = c('Provider','Degree')
    
    # Calculate Betweeenness
    btwn = betweenness(bn.provider)
    btwn = tibble(names(btwn), btwn)
    colnames(btwn) = c('Provider','Betweenness')
    
    # Calculate Values of the First Eigenvector of the Graph Matrix
    eign = eigen_centrality(bn.provider)$vector
    eign = tibble(names(eign), eign)
    colnames(eign) = c('Provider','Eigenvector')
    
    # Calculate Average Nearest Neighbors
    ann = knn(bn.provider)
    ann = ann$knn
    ann = tibble(names(ann), ann)
    colnames(ann) = c('Provider','Avg.NN')
    
    # Add to list by state
    deglist[[state]] = deg
    btwnlist[[state]] = btwn 
    eigenlist[[state]] = eign 
    annlist[[state]] = ann 
}
#############################################################################

prodocDeg <- dplyr::bind_rows(deglist)
prodocBtwn <- dplyr::bind_rows(btwnlist)
prodocEign <- dplyr::bind_rows(eigenlist)
prodocANN <- dplyr::bind_rows(annlist)

```

```{r}

propatDeg_clean = propatDeg %>% group_by(Provider) %>% summarise(patDegMax = max(Degree, na.rm=TRUE))
propatBtwn_clean = propatBtwn %>% group_by(Provider) %>% summarise(patBtwnMean = mean(Betweenness, na.rm=TRUE))
propatEign_clean = propatEign %>% group_by(Provider) %>% summarise(patEignMean = mean(Eigenvector, na.rm=TRUE))
propatANN_clean = propatANN %>% group_by(Provider) %>% summarise(patMANN = mean(Avg.NN, na.rm=TRUE))

prodocDeg_clean = prodocDeg %>% group_by(Provider) %>% summarise(docDegMax = max(Degree, na.rm=TRUE))
prodocBtwn_clean = prodocBtwn %>% group_by(Provider) %>% summarise(docBtwnMean = mean(Betweenness, na.rm=TRUE))
prodocEign_clean = prodocEign %>% group_by(Provider) %>% summarise(docEignMean = mean(Eigenvector, na.rm=TRUE))
prodocANN_clean = prodocANN %>% group_by(Provider) %>% summarise(docMANN = mean(Avg.NN, na.rm=TRUE))


propatNet = propatDeg_clean %>% 
  left_join(propatBtwn_clean, by='Provider') %>% 
  left_join(propatEign_clean, by='Provider') %>% 
  left_join(propatANN_clean, by='Provider')

prodocNet = prodocDeg_clean %>% 
  left_join(prodocBtwn_clean, by='Provider') %>% 
  left_join(prodocEign_clean, by='Provider') %>% 
  left_join(prodocANN_clean, by='Provider')

write_csv(prodocNet,'../../prodocNet.csv')
write_csv(propatNet,'../../propatNet.csv')

```

```{r}
source('getNet.R')
bnet = prodoc(data, c('Alaska'), 'all')
bn.pr = bipartite.projection(bnet)
bn.provider <- bn.pr$proj2

deg = degree(bn.provider)
str = strength(bn.provider)
ann = knn(bn.provider)
ann = ann$knn

deg = tibble(names(deg), deg)
str = tibble(names(str), str)
ann = tibble(names(ann), ann)

colnames(deg) = c('Provider','Degree')
colnames(str) = c('Provider','Strength')
colnames(ann) = c('Provider','Avg.NN')

deg %>% left_join(ann, by = 'Provider')

```
```{r}
# wc = cluster_fast_greedy(bnet)
# modularity(wc)
# membership(wc)
# 
# #plot(distance_table(bn.provider, directed = FALSE))
# mean_distance(bn.provider)

# By default weighted by graph edge weights unless passed
# Algo is chosen to take into account edge weights
bnet = propat(data, c('Oklahoma'), 'all')
bn.pr = bipartite.projection(bnet)
bn.provider <- bn.pr$proj2

paths = data.frame(distances(bn.provider, v=V(bn.provider), to = V(bn.provider)))
isolated = which(degree(bn.provider)==0)
paths_rowdel = paths[-isolated[[1]],]
paths_coldel = paths_rowdel[,-isolated[[1]]]
paths_mean = rowSums(paths_coldel)/(length(paths_coldel)-1)
paths_mean

```

```{r}
bnet = prodoc(data, c('Hawaii'), 'all')
bn.pr = bipartite.projection(bnet)
bn.provider <- bn.pr$proj2
g = connect(bn.provider,2)

ggraph(bn.provider, layout='kk')+
    geom_edge_link0(alpha=0.5, edge_colour = "grey66") + 
    geom_node_point(aes(color = fraud, size = size)) +
    #geom_node_point() +
    scale_size_continuous(range = c(1,5), guide=FALSE)+
    theme_graph() +
    theme(legend.position = "bottom")


ggraph(g, layout='kk')+
    geom_edge_link0(alpha=0.5, edge_colour = "grey66") + 
    geom_node_point(aes(color = fraud, size = size)) +
    #geom_node_point() +
    #scale_size_continuous(range = c(1,5), guide=FALSE)+
    theme_graph() +
    theme(legend.position = "bottom")

```
```{r}
vignette('ergm-term-crossRef')
```
```{r}
crnd <- runif(500,1,8)
cmp_prp <- sapply(crnd,function(x)
max(clusters(erdos.renyi.game(n=1000, p=x/999))$csize)/1000)

smoothingSpline <- smooth.spline(crnd,cmp_prp, spar=0.25)
plot(crnd,cmp_prp,col='grey60', xlab="Avg. Degree",
ylab="Largest Component Proportion") 
lines(smoothingSpline,lwd=1.5)
```
```{r}
library(lattice)

n_vect <- rep(c(50,100,500,1000,5000),each=50) 
g_diam <- sapply(n_vect,function(x) diameter(erdos.renyi.game(n=x,p=6/(x-1))))
bwplot(g_diam ~ factor(n_vect), panel = panel.violin,
    xlab = "Network Size", ylab = "Diameter")
```


```{r}
ggraph(bnet, layout ='stress')+
    geom_edge_link0(alpha=0.5, edge_colour = "grey66", aes(width = weights)) + 
    #geom_node_point(aes(color = fraud, size = size), shape = V(bnet)$shape) +
    geom_node_point(aes(
      #fitler = size >= 10,
      color = fraud,
      size = size), shape = V(bnet)$shape) +
    geom_node_text(aes(filter = size >= 50, label = name, size=3),family="serif", repel=TRUE)+
    scale_color_brewer(palette = "Dark2")+
    scale_edge_width_continuous(range = c(0.2,3), guide=FALSE)+
    scale_fill_manual(values = palette) +
    scale_size_continuous(range = c(1,5), guide=FALSE)+
    theme_graph() +
    theme(legend.position = "bottom")
  
    #ggsave(filename=paste0('./visualizations/networks/pb_5_200_sugiyama.png'),plot=last_plot())
}
```

```{r}
bnet = propat(data, c('Rhode Island'), 'all')
bn.pr = bipartite.projection(bnet)

bn.patient <- bn.pr$proj1
bn.provider <- bn.pr$proj2

ggraph(bnet, layout ='stress')+
    geom_edge_link0(alpha=0.5, edge_colour = "grey66", aes(width = weights)) + 
    #geom_node_point(aes(color = fraud, size = size), shape = V(bnet)$shape) +
    geom_node_point(aes(
      #fitler = size >= 10,
      color = fraud,
      size = size), shape = V(bnet)$shape) +
    geom_node_text(aes(filter = size >= 50, label = name, size=3),family="serif", repel=TRUE)+
    scale_color_brewer(palette = "Dark2")+
    scale_edge_width_continuous(range = c(0.2,3), guide=FALSE)+
    scale_fill_manual(values = palette) +
    scale_size_continuous(range = c(1,5), guide=FALSE)+
    theme_graph() +
    theme(legend.position = "bottom")

ggraph(bn.patient, layout ='stress')+
    geom_edge_link0(alpha=0.5, edge_colour = "grey66") + 
    #geom_node_point(aes(color = fraud, size = size), shape = V(bnet)$shape) +
    geom_node_point(aes(
      #fitler = size >= 10,
      #color = fraud,
      size = size)) +
    geom_node_text(aes(filter = size >= 50, label = name, size=3),family="serif", repel=TRUE)+
    scale_color_brewer(palette = "Dark2")+
    scale_edge_width_continuous(range = c(0.2,3), guide=FALSE)+
    scale_fill_manual(values = palette) +
    scale_size_continuous(range = c(1,5), guide=FALSE)+
    theme_graph() +
    theme(legend.position = "bottom")

ggraph(line.graph(bn.patient), layout ='sugiyama')+
    geom_edge_link0(alpha=0.5, edge_colour = "grey66") + 
    #geom_node_point(aes(color = fraud, size = size), shape = V(bnet)$shape) +
    geom_node_point() +
    scale_color_brewer(palette = "Dark2")+
    scale_edge_width_continuous(range = c(0.2,3), guide=FALSE)+
    scale_fill_manual(values = palette) +
    #scale_size_continuous(range = c(1,5), guide=FALSE)+
    theme_graph() +
    theme(legend.position = "bottom")

ggraph(bn.provider, layout ='sugiyama')+
    geom_edge_link0(alpha=0.5, edge_colour = "grey66") + 
    #geom_node_point(aes(color = fraud, size = size), shape = V(bnet)$shape) +
    geom_node_point(aes(
      #fitler = size >= 10,
      color = fraud,
      size = size)) +
    scale_color_brewer(palette = "Dark2")+
    scale_edge_width_continuous(range = c(0.2,3), guide=FALSE)+
    scale_fill_manual(values = palette) +
    scale_size_continuous(range = c(1,5), guide=FALSE)+
    theme_graph() +
    theme(legend.position = "bottom")


```





```{r}
bn.pr <- bipartite.projection(bnet)
bn.patient <- bn.pr$proj1 
bn.provider <- bn.pr$proj2 
graph.density(bn.patient)
#get.adjacency(bn.patient,sparse=FALSE,attr="weight")
```
```{r}
shapes <- c("circle","square") 
colors <- c("blue","red")
op <- par(mfrow=c(1,2)) 
# plot(bn.patient,vertex.color="blue",
#      vertex.shape="circle",main="Patients", 
#      edge.width=E(bn.patient)$weight*2, 
#      vertex.size=15,vertex.label.degree=-pi/2, 
#      vertex.label.dist=1.2,vertex.label.cex=1)
# plot(bn.provider,vertex.color="red", 
#      vertex.shape="square",main="Providers", 
#      edge.width=E(bn.patient)$weight*2, 
#      vertex.size=15,vertex.label.degree=-pi/2, 
#      vertex.label.dist=1.2,vertex.label.cex=1)


ggraph(bn.patient, layout='stress') +
  geom_edge_link0(color="gray50", width=0.8, alpha=0.5) +  
  geom_node_point() +
  geom_node_text(aes(filter = size >= 10, label = name, size=3),family="serif", repel=TRUE)+
  theme_graph() +
  theme(legend.position = "bottom")


ggraph(bn.provider, layout='stress') +
  geom_edge_link0(color="gray50", width=0.8, alpha=0.5) +
  geom_node_text(aes(filter = size >= 10, label = name, size=3),family="serif", repel=TRUE)+
  geom_node_point(aes(color = fraud, size = size)) +
  scale_size_continuous(range = c(1,5), guide=FALSE)+
  theme_graph() +
  theme(legend.position = "bottom")
par(op)
```

```{r}



df.prom <- data.frame(
  btw = betweenness(bn.provider), 
  evc = evcent(bn.provider),
  inf = infocent(bn.provider), 
  flb = flowbet(bn.provider)
)
```



## Great example of how a new metric can be created... though maybe this can also be done easliy with dataframe groupings.. 
```{r}
for (i in 161:1365) {
  V(h1)[i]$totrating <- sum(V(h1)[nei(i)]$IMDBrating)
}

pop_actor <- data.frame(cbind(Actor = V(h1)[type==FALSE & totrating > 40]$name, 
                              Popularity = V(h1)[type==FALSE & totrating > 40]$totrating)) 

pop_actor[order(pop_actor$Popularity,decreasing=TRUE),]

scatter.smooth(num,avgpop,col="lightblue", 
               ylim=c(2,10),span=.8, xlab="Number of Movies", ylab="Avg. Popularity")
```


```{r}
h1.pr <- bipartite.projection(h1) 
h1.act <- h1.pr$proj1
h1.mov <- h1.pr$proj2
h1.act
```

```{r}
op <- par(mar = rep(0, 4)) 
plot(bn.provider,vertex.color="red", 
     vertex.shape="circle", 
     vertex.size=(E(bn.provider)$weight+1)/2, 
     vertex.label=NA)

par(op)
no.clusters(bn.provider)

```

```{r}
bn.provider <- induced.subgraph(bn.provider, vids=clusters(bn.provider)$membership==1)
plot(bn.provider,vertex.color="red", 
     edge.width=sqrt(E(bn.provider)$weight), 
     vertex.shape="circle", 
     vertex.size=E(bn.provider)$weight, 
     vertex.label=NA)

```


```{r}
h1.pr <- bipartite.projection(binet) 
h1.act <- h1.pr$proj1
h1.mov <- h1.pr$proj2
h1.act
```


```{r}
par(mar=c(0,0,0,0))

render.d3movie(doc_net, usearrows = F, displaylabels = F, bg="#111111", 
       vertex.border="#ffffff", 
       #vertex.col =  net3 %v% "col",
       #vertex.cex = (net3 %v% "audience.size")/8, 
       edge.lwd = (net3 %e% "weight")/3, 
       edge.col = '#55555599',
       vertex.tooltip = paste("<b>Name:</b>", (net3 %v% 'label')), 
                              #"<br>",
                              #"<b>Type:</b>", (net3 %v% 'type.label')),
       edge.tooltip = paste("<b>Connection to Source:</b>", (net3 %e% 'Connection'), "<br>", 
                            "<b>Number of Claims Filed:</b>", (net3 %e% "weight" ) ),
       launchBrowser=F, filename="Doc-Network.html")
```



```{r}
edges = mutate(edges, width = weight/5 + 1)

visNetwork(nodes,edges) %>% 
  visIgraphLayout(layout = "layout_with_fr") %>% 
  visEdges(arrows="middle")
```

```{r}
prpat = function(data){

  data.filt = data %>% 
    dplyr::select(Provider, PotentialFraud, BeneID, InscClaimAmtReimbursed,WhetherDead) %>%
    group_by(Provider, PotentialFraud, BeneID,WhetherDead) %>% 
    summarise(weights = sum(InscClaimAmtReimbursed)) %>% data.frame()
  
  ## Get Provider | Beneficiary
  connections = data.filt %>% dplyr::select(Provider,BeneID,WhetherDead,weights)
  ## Create bipartite graph
  Bnet <- graph_from_data_frame(connections,directed=FALSE)
  ## Add attribues
  shapes <- c(21,15)
  fraud = data.filt %>% select(Provider,PotentialFraud)
  V(Bnet)$type <- V(Bnet)$name %in% connections[,1]
  return(Bnet)
}
```

```{r}
forceNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
             NodeID = "label", Group = "id", Value = "weight", 
             opacity = 1, fontSize = 16, zoom = TRUE)
```
```{r}
sankeyNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
              NodeID = "label", Value = "weight", fontSize = 16, unit = "Letter(s)")
```
```{r}
netmat1 <- rbind(c(0,1,1,0,0), c(0,0,1,1,0), c(0,1,0,0,0), c(0,0,0,0,0), c(0,0,1,0,0))
rownames(netmat1) <- c("A","B","C","D","E") 
colnames(netmat1) <- c("A","B","C","D","E")
net1 <- network(netmat1,matrix.type="adjacency") 
class(net1)
```

```{r}
prpat = function(data, state, county){
  if(county == 'all'){
    data.filt = 
      data %>% filter(State %in% state)
  } else {
    data.filt = 
      data %>% filter(State %in% state, County %in% county)
  }
  data.filt = 
    data.filt %>%
    dplyr::select(Provider, BeneID, TotalClaim) %>%
    group_by(Provider,BeneID) %>% 
    summarise(weights = sum(TotalClaim)) %>% data.frame()
  
  ## Get Provider | Beneficiary
  connections = data.filt
  ## Create bipartite graph
  Bnet <- graph_from_data_frame(connections,directed=FALSE)
  return(Bnet)
}
# palette = c(green "#009E73",purple "#CC79A7",blue: "#0072B2", red:"#D55E00")

plotProPat = function(bnet, state, county, layout){
  
  ggraph(bnet, layout = layout)+
    geom_edge_link0(
      edge_alpha=0.3, 
      edge_color = E(bnet)$color, 
      aes(edge_width = weights)) + 
    geom_node_point(
      aes(size = size), 
      shape = V(bnet)$shape, 
      color = V(bnet)$color) +
    geom_node_text(aes(filter = size >= 100, label = name, size=3),family="serif", repel=TRUE)+
    scale_edge_width_continuous(range = c(0.2,4), guide=FALSE)+
    scale_size_continuous(range = c(2,6), guide=FALSE)+
    theme_graph()
}

plotActor = function(net, title, layout = 'kk', actor = 'provider'){

  if (actor=='provider') {
    shape = 15
  } else if (actor == 'patient') {
    shape = 21
  } else if (actor == 'doctor') {
    shape = 17
  }
  
  
  ggraph(net, layout = layout)+
    geom_edge_link0(edge_alpha=0.5, edge_colour = "grey66") + 
    geom_node_point(
    aes(size = size),
    color = V(net)$color,
    shape = shape) + 
    scale_edge_width_continuous(range = c(0.2,3), guide=FALSE)+
    scale_size_continuous(range = c(2,6), guide=FALSE) +
    theme_graph() +
    ggtitle(title)
}

```

```{r}
bnet = prpat(data)
bn.pr = bipartite.projection(bnet, remove.type = FALSE)

bn.patient <- bn.pr$proj1
bn.provider <- bn.pr$proj2

plotProPat(bnet, 'Oklahoma',100,'stress')
plot1 = plotActor(bn.patient, 'Patient', layout = 'mds', actor='patient')
plot2 = plotActor(bn.provider, 'Provider', layout = 'stress', actor='provider')
plot1 + plot2
plotActor(bn.provider, 'title', layout = 'tree', actor='doctor')
```

```{r}

claimTrack = read_csv('../data/claimTrack.csv')
```
```{r}

edges = data %>% select(BeneID,Provider,ClaimID) %>% 
  group_by(BeneID,Provider) %>% tally() %>% graph.data.frame(directed = FALSE)


#state = data %>% distinct(State)
edges = claimTrack %>% 
  select(Provider_S,Provider_R,ClaimMultiplier) %>% data.frame()

dnet = edges %>% graph.data.frame(directed = TRUE)
V(dnet)$size <- sqrt(strength(dnet))
V(dnet)$fraud = ifelse(V(dnet)$name %in% target[,1],target[,2],'?')

V(dnet)$color = edges %>% pivot_longer(cols=c(Provider_S,Provider_R)) %>% inner_join(target,by=c('value'='Provider')) %>% select(color) %>% pull


#dnet = simplify(dnet)
#dnet = delete_isolates(dnet)

```

```{r}
dnet %>% ggraph(.,layout = 'stress')+
    geom_edge_fan0(arrow = arrow(angle = 30, length = unit(0.02, "inches"),
                              #ends = "last", 
                              type = "closed"),
                   alpha=0.5, 
                   edge_color="grey66",
                   aes(edge_width = ClaimMultiplier))+
    geom_node_point(
      aes(size = size),
      shape = 20,
      alpha=0.6,
      color = V(dnet)$color
      #color = 'blue'
      ) +
    #geom_node_text(aes(filter = size >= 15, label = name, size=3),family="serif", repel=TRUE)+
    scale_edge_width_continuous(range = c(0.5,2), guide=FALSE)+
    scale_size_continuous(range = c(1,5), guide=FALSE)+
    theme_graph()

ggsave(filename=paste0('../visualizations/networks/outpatientdup.png'),plot=last_plot())
```

```{r}
#state = data %>% distinct(State)
edges = claimTrack %>% 
  #filter(State_S %in% state, State_R %in% c('New York')) %>% 
  select(Doctor_S,Doctor_R) %>% data.frame()


dnet = edges %>% graph.data.frame(directed = TRUE)
#dnet = simplify(dnet)
#V(dnet)$type <- ifelse(V(dnet)$name %in% edges[,1],'Sender','Receiver')

V(dnet)$size <- sqrt(strength(dnet))
# senders = V(dnet)[type=='Sender']
# receivers = V(dnet)[type=='Receiver']
# 
# 
# E(dnet)[senders %--% receivers]$color = "#e65247" # red
# E(dnet)[FraudNo %--% Patients]$color = "#57bf37" #green
#V(dnet)$fraud = ifelse(V(dnet)$name %in% target[,1],target[,2],'?')


#V(dnet)$color = edges %>% pivot_longer(cols=c(Provider_S,Provider_R)) %>% inner_join(target,by=c('value'='Provider')) %>% select(color) %>% pull
```

```{r}
g = dnet %>% ggraph(.,layout = 'stress')+
    geom_edge_fan0(arrow = arrow(angle = 30, length = unit(0.03, "inches"),
                              ends = "last", type = "closed"),alpha=0.5, edge_color='blue')+
    geom_node_point(
      aes(size = size),
      shape = 20,
      alpha=0.6,
      #color = V(dnet)$color
      #color = 'blue'
      ) +
    #geom_node_text(aes(filter = size >= 15, label = name, size=3),family="serif", repel=TRUE)+
    scale_edge_width_continuous(range = c(0.2,4), guide=FALSE)+
    scale_size_continuous(range = c(2,4), guide=FALSE)+
    theme_graph()

ggsave(filename='../doctordup.png',plot=g)

```

